|

### 2023-10-03 manuscript_BE/manuscript_BE.Rmd
BayesianTools was not getting a reasonable response from the LH function. Now it seems to be fixed. Ready for new sims

Low cleaner fish relative abundance yields different predictions 
from a model with only chaining and with penalty.
The model with only chaining predicts a low preference fpr the visitor when
cleaner fish relative abundance is low (Fig. \ref{fig:pred} c). In contrast,
the models including penalty (with and without chaining) predict high 
preference for the visitor option (Fig. \ref{fig:pred} a and e).
For intermediate and high cleaner relative abundances the predictions 
are similar for all three models. Intermediate relative abundance 
trigger a high preference for the visitor; while low abundances trigger
low preference for the visitor (Fig. \ref{fig:pred}a,b,e). 
Note, however, we calculated 
preferences shown in figure \ref{fig:pred} left panels by using only the model 
of the posterior distributions, and by holding constant the balance between 
resident and visitors' abundances. Panels on the right, show how close 
predictions are from the observed data, allowing the balance between 
client types to vary and using a set of samples from the posterior 
distribution.

Visitor leaving probability has an overall 
positive effect on the probability of choosing the visitor
clients on all three models. All three models predict an increase preference 
for visitors as the visitor probability increases  (Fig. \ref{fig:pred}).

@@

While all three models captured well the positive relationship between visitor 
leaving behavior and cleaner fish performance in
the market task [@triki_Biological_2019], only the chaining mechanism 
predicted that cleaner fish performance in the task should be low in 
habitats with low cleaner-to-client ratios, regardless of the 
visitor leaving probability. In contrast, models including 
negative reward predicted the highest performance in the ephemeral 
reward task when relative cleaner fish abundance is low, particularly 
together with a high probability of visitor leaving (Fig. \ref{fig:pred}).
Low relative cleaner fish abundances mean the market has an excess of demand for
cleaning services. In the models, this translates to a cleaning station
that is frequently full. Thus, when a visitor leaves, it is likely that the
cleaner fish will have access to another client in the next step. Therefore, 
there will not be much difference in future reward between choosing 
a visitor and a resident, and cleaners will not develop a preference for the
visitor in these conditions. On the other hand, the effect of negative reward 
on cleaner fish preference is the opposite, as in a busy cleaning station, to
that of chaining. Cleaner fish will get more often the resident-visitor
state and will develop a preference for the visitor faster. 
At high cleaner fish abundances, the resident-visitor state
becomes so rare that neither mechanism is very efficient 
at generating a preference for visitors. When facing the 
resident-visitor choice, it is still best to choose the visitor; however,
the learning machinery will not be able to develop this preference
efficiently. Overall, the models suggest that chaining is the cognitive
mechanism that allows cleaner fish to adaptively adjust to their 
biological market ecological conditions.

>>>>

Low cleaner fish relative abundance yields different predictions 
from a model with only chaining and with penalty.
The model with only chaining predicts a low preference fpr the visitor when
cleaner fish relative abundance is low (Fig. \ref{fig:predPAA} c). In contrast,
the models including penalty (with and without chaining) predict high 
preference for the visitor option (Fig. \ref{fig:predFAA} a and e).
For intermediate and high cleaner relative abundances the predictions 
are similar for all three models. Intermediate relative abundance 
trigger a high preference for the visitor; while low abundances trigger
low preference for the visitor (Fig. \ref{fig:predFAA}a,b,e). 
Note, however, we calculated 
preferences shown in figure \ref{fig:predFAA} left panels by using only the model 
of the posterior distributions, and by holding constant the balance between 
resident and visitors' abundances. Panels on the right, show how close 
predictions are from the observed data, allowing the balance between 
client types to vary and using a set of samples from the posterior 
distribution.

Visitor leaving probability has an overall 
positive effect on the probability of choosing the visitor
clients on all three models. All three models predict an increase preference 
for visitors as the visitor probability increases  (Fig. \ref{fig:predFAA}).

@@

While all three models captured well the positive relationship between visitor 
leaving behavior and cleaner fish performance in
the market task [@triki_Biological_2019], only the chaining mechanism 
predicted that cleaner fish performance in the task should be low in 
habitats with low cleaner-to-client ratios, regardless of the 
visitor leaving probability. In contrast, models including 
negative reward predicted the highest performance in the ephemeral 
reward task when relative cleaner fish abundance is low, particularly 
together with a high probability of visitor leaving (Fig. \ref{fig:predFAA}).
Low relative cleaner fish abundances mean the market has an excess of demand for
cleaning services. In the models, this translates to a cleaning station
that is frequently full. Thus, when a visitor leaves, it is likely that the
cleaner fish will have access to another client in the next step. Therefore, 
there will not be much difference in future reward between choosing 
a visitor and a resident, and cleaners will not develop a preference for the
visitor in these conditions. On the other hand, the effect of negative reward 
on cleaner fish preference is the opposite, as in a busy cleaning station, to
that of chaining. Cleaner fish will get more often the resident-visitor
state and will develop a preference for the visitor faster. 
At high cleaner fish abundances, the resident-visitor state
becomes so rare that neither mechanism is very efficient 
at generating a preference for visitors. When facing the 
resident-visitor choice, it is still best to choose the visitor; however,
the learning machinery will not be able to develop this preference
efficiently. Overall, the models suggest that chaining is the cognitive
mechanism that allows cleaner fish to adaptively adjust to their 
biological market ecological conditions.
